---
title: "A Systematic Review of the Research Literature on Youth Recidivism in Education"
author: 
  - "Nicholas Angelo"
  - "Howard University"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true  # Enable floating TOC in the sidebar
    number_sections: true
    theme: cerulean
    always_allow_html: true
    self_contained: true
editor_options:
  chunk_output_type: console
  markdown:
    wrap: sentence
---

```{r setup, include=F}
knitr::opts_chunk$set(
  echo = TRUE, # By default, hide code; set to TRUE to see code
  fig.pos = 'th', # Places figures at top or here
  out.width = '100%', dpi = 300, # Figure resolution and size
  fig.env="figure"
) # Latex figure environment

options(knitr.table.format = "latex") # For kable tables to write LaTeX table directly
```

# Libraries and packages

```{r, message=F, warning=F}
## set up, load libraries
library(dplyr)
library(readtext)
library(tidyverse)
library(here)
library(gt)
library(ggplot2)
library(dplyr)
library(knitr)
library(readr)
library(kableExtra)
library(bibliometrix)
library(tidyverse)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(quanteda)
library(stringr)
library(tidytext)
library("quanteda.textmodels")
library("quanteda.textstats")
library("quanteda.textplots")
require(quanteda.corpora)
here::i_am("youth_rec.Rmd")
```

# LITERATURE REVIEW

In this section, we provide a summary of our scoping process in the preparation of the systematic literature review.

type my summary

# RESEARCH QUESTIONS

1.  What is the intellectual and conceptual structure of research on ...?

# METHOD

| Code | Criteria                                                                     |
|-------------------|-----------------------------------------------------|
| IC1  | Article contains keywords in the title (TI) or abstract (AB)                 |
| IC2  | Article published between 2015 and 2024                                      |
| IC3  | Article originally written in English                                        |
| IC4  | Article is a journal article                                                 |
| IC5  | Article purpose or core questions center on the topical subjects of analysis |

: Inclusion and exclusion criteria for the study

## Scoping

TBD

## Review

Key Columns of Interest:

-   AU: Authors of the publication

-   AB: Abstract text

-   TI: Title of the publication

-   AU_CO: Countries of the authors

-   SC: Subject categories (e.g., "Education & Educational Research")

-   PY: Publication year

-   TC: Total citations

## Reduction

TBD

# ANALYTIC FRAMEWORK

```{r, echo=F, include=T}
# Create the framework
tmp = DiagrammeR::grViz('digraph model {

    graph [layout = dot, overlap = true]
    
    node [shape=box]
    {"Scoping"} -> {"Review"} -> {"Reduction"};
 
    node [shape=box]
    {"Patterns = 6"} -> {"Sources = TDB"} -> docs;
    
    node [shape=box]
    docs [label=<Documents, n = TBD>];
    
# `edge` statements
 
    edge [minlen = 2]
    docs -> {"Concepts" -> Themes}

 }') 

# Display the graph
tmp

# Export to SVG
tmp_svg = DiagrammeRsvg::export_svg(tmp)

# Convert SVG to raw vector
tmp_raw = charToRaw(tmp_svg)

```

# DATA

Loading the text file.

```{r, message=F, warning=F}
data <- readtext("savedrecs-2.txt") # Load the data
M <- convert2df(file=data, dbsource= "wos", format= "plaintext")
dim(M)

# create an object of the study results
results <- biblioAnalysis(M, sep = ";") # entire data set

options(width=100)
S <- summary(object = results, k = 10, pause = F)
```

```{r, message=F, warning=F}

```
